---
title: "analysis"
author: "sjgknight"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyr,
               magrittr,
               dplyr,
               tibble,
               wikkitidy, 
               reactable,
               reactablefmtr)

custom <- list.files(here::here('R/'),full.names = T)

purrr::quietly(
  lapply(custom, source)
)

rm(custom)

```

## Queries

Core policies extacted from initial manual analysis. 

```{r define_queries}

# ==============================================================================
# Params
# ==============================================================================

prepend <- c("WP:", "Wikipedia:")

namespace <- "1" # article is 0, talk is 2, https://en.wikipedia.org/wiki/Wikipedia:Namespace

articles <- c("Origin of SARS-CoV-2",
              "COVID-19 drug repurposing research",
              "COVID-19",
              "Face masks during the COVID-19 pandemic")

format = "json"

policies_core <- c("MEDRS",
                   "NOTRS", 
                   "SPS", 
                   "BLOGS",
                   "QUESTIONABLE", 
                   "QUESTIONED", 
                   "SPONSOR", 
                   "SPONSORED", 
                   "USERG", 
                   "UGC", 
                   "USERGENERATED", 
                   "QS", 
                   "NOR", 
                   "NPOV", 
                   "DUE", 
                   "MEDSCI", 
                   "MEDPOP", 
                   "MEDORG",
                   "BIO", 
                   "MEDASSESS",
                   "CONSENSUS",
                   "FALSEBALANCE", 
                   "FRINGELEVEL",
                   "FRINGE", 
                   "SCIRS", 
                   "MEDFAQ", 
                   "RS",
                   "RSUW",
                   "EVALFRINGE",
                   "DESCF", 
                   "FDESC", 
                   "PROFRINGE", 
                   "RSP",
                   "RS/P",
                   "RSPS",
                   "CIR",
                   "COMPETENCE",
                   "PARITY")
  

# ==============================================================================
# BUILD SEARCH QUERIES
# ==============================================================================

# assemble your OR conditions
policy_terms <- paste(paste0("WP:", policies_core), paste0("Wikipedia:", policies_core), collapse = " OR ", sep = " OR ")

policy_and_page <- paste(policy_terms, 
                         paste0("prefix:\"", "Talk:", articles, "\""), 
                         sep = " ")


# ==============================================================================
# STEP 1: RUN INITIAL SEARCH
# ==============================================================================

if(file.exists("output/wikipedia_raw_results.rds")){
  message("Loaded existing raw results from output/wikipedia_raw_results.rds")
  
  results <- readRDS("output/wikipedia_raw_results.rds")

} else {
  message("No existing raw results found, proceeding to run queries.")

  results <- purrr::map_dfr(policy_and_page,
                          ~ wiki_get_query(
                            policy_and_page_string = .x,
                            namespace = 1,
                            srlimit = 50,
                            max_len = 280
                            ) # %>%
        #mutate(original_query = .x)  # add a column with the policy_and_page string
  )
  saveRDS(results, "output/wikipedia_raw_results.rds")
}

# ==============================================================================
# ==============================================================================
# Get full content and save it
# ==============================================================================
# ==============================================================================

if(file.exists("output/wikipedia_full_results.rds")){
  message("Loaded existing highlighted results from output/wikipedia_highlighted_results.rds")
  
  results_with_content <- readRDS("output/wikipedia_full_results.rds")

} else {
  message("No existing highlighted results found, proceeding to create full content.")
  
  # ==============================================================================
  # STEP 2: GET SECTION INDICES and Content for sections if available, else pages
  # ==============================================================================
  
  results_with_content <- results %>%
    mutate(
      # Step 3a: fetch section index (if sectiontitle exists)
      section_index = map2_chr(pageid, sectiontitle, ~ {
        if (is.na(.y)) return(NA_character_)
        secs <- wiki_get_structure(.x)
        matched <- secs$index[secs$line == .y]
        if (length(matched) == 0) NA_character_ else matched
      })
    )
  
  # ==============================================================================
  # STEP 3: FETCH HTML CONTENT and Wikitext
  # ==============================================================================
  results_with_content <- results_with_content %>%
    mutate(
      content_html = map2_chr(pageid, section_index, ~ {
        wiki_get_html(.x, if (is.na(.y) || .y == "") NULL else .y)
      })
    )
  
  results_with_content <- results_with_content %>%
    mutate(
      # Step 3b: fetch page content (whole page if section_index is NA)
      content = if(any(is.na(section_index), section_index == "")) {
                     map_chr(pageid, ~ wiki_get_wikitext(.x)$content)
      } else {
        map2_chr(pageid, section_index, ~ wiki_get_wikitext(.x, if (.y == "") NULL else .y)$content)
      }
  )
  
  # results_with_content <- results_with_content %>%
  #   mutate(
  #     content_html = map_chr(content, ~ 
  #                              wikitext_to_html(.x)
  #     ))
  
  # ==============================================================================
  # STEP 4: EXTRACT WP POLICIES
  # ==============================================================================
  
  
  results_with_content <- results_with_content %>%
    mutate(
      wp_policies = map(content_html, wiki_extract_policies),
      num_policies = map_int(wp_policies, length)
    )
  
  message(sprintf("Extracted policies from %d pages", 
                  sum(results_with_content$num_policies > 0)))
  
  # ==============================================================================
  # STEP 5: HIGHLIGHT SEARCH TERMS
  # ==============================================================================
  
  results_with_content <- results_with_content %>%
    mutate(
       content_html = wikipolicy_mark(content_html, policies_core)
       ) %>%
    mutate(content_html = str_replace_all(
      content_html,
      'href=["\'](?!https?:|mailto:|#)/?([^"\']+)["\']',
      'href="https://wikipedia.org/\\1"')
  )

   # ==============================================================================
  # Save output
  # ==============================================================================
  
  saveRDS(results_with_content, "output/wikipedia_full_results.rds")

}

  
# ==============================================================================
# STEP 6: Filter: Remove duplicate pages (where multiple policies trigger), and remove from html content without policies
# ==============================================================================

if(file.exists("output/wikipedia_filtered_results.rds")){
  results_filtered_content <- readRDS("output/wikipedia_filtered_results.rds")
  message("Loaded existing filtered results from output/wikipedia_filtered_results.rds")
} else {
  message("No existing filtered results found, proceeding to create new filtered results.")
  
  # Apply filtering
results_filtered_content <- results_with_content %>%
  select(title, timestamp, pageid, sectiontitle, content_html, wp_policies, num_policies) %>%
  unique()

# Here idea was to remove sections that aren't relevant but it turned out harder than I wanted

results_filtered_content <- results_filtered_content %>%
   mutate(
     content_filtered = wiki_filter_policy_sections(content_html, policy_patterns = 'class="[^"]*wp-policy-link[^"]*"'),
     policies_in_filtered = map(content_filtered, wiki_extract_policies),
     num_policies_filtered = map_int(policies_in_filtered, length)
   ) %>%
  dplyr::filter(num_policies_filtered > 0)

saveRDS(results_filtered_content, "output/wikipedia_filtered_results.rds")

}



```




## Policy pieces

We only extract based on the initial list. But there's a much bigger list available. 

```{r policyextraction}

policies_all <- results_filtered_content %>%
  select(wp_policies) %>%
  flatten() %>% 
  unlist() %>% 
  unique()

policies_filtered <- results_filtered_content %>% 
  select(policies_in_filtered) %>%
  flatten() %>% 
  unlist() %>% 
  unique()

# ==============================================================================
# EXTRACT 1: Policy hierarchy to get unique policies and their sub-policy shortcuts
# ==============================================================================
if(file.exists("output/policy_result.rds")){
  message("Loaded existing policy hierarchy from output/policy_hierarchy.rds")
  
  policy_use <- readRDS("output/policy_result.rds")

  policy_expansive <- readRDS("output/policy_expansive.rds")

} else {
  message("No existing policy hierarchy found, proceeding to create new hierarchy.")

  policy_use <- paste("WP:",policies_core) %>% 
    stringr::str_remove(" ") %>%
    build_policy_hierarchy(include_referenced = TRUE, max_depth = 1)
  
  readr::write_rds(policy_use, "output/policy_result.rds")
  
  policy_expansive <- policies_filtered %>% 
    stringr::str_remove(" ") %>%
    build_policy_hierarchy(include_referenced = TRUE, max_depth = 1)

  # Your original code - this should work fine
  policy_expansive <- policy_expansive %>% 
    mutate(categories = map(wikitext, wiki_extract_parts, part = "category"),
           templates = map(wikitext, wiki_extract_parts, part = "template"))
  
    readr::write_rds(policy_expansive, "output/policy_expansive.rds")

}


# ==============================================================================
# EXTRACT 2: Policies and subpolicies
# ==============================================================================

if(file.exists("output/policy_pages_nested.rds")){
  message("Loaded existing nested policy pages from output/policy_pages_nested.rds")
  
  policy_pages_nested <- readRDS("output/policy_pages_nested.rds")

  all_subpolicies <- readr::read_rds("output/all_subpolicies.rds")

} else {
  message("No existing nested policy pages found, proceeding to create new nested structure.")
  
  # Step 1: Extract heading-to-shortcut mappings (nested structure)
  policy_pages_nested <- policy_use %>%
    mutate(
      # Extract shortcuts mapped to headings for each page
      shortcut_sections = map2(wikitext, page_title, 
                               ~wiki_extract_title(.x, page_title = .y) %>%
                                 select(-line_num) %>%
                                 unique()
      )
    )
  
  # Step 2: Get section structure for pages (if not already present)
  if (!"sections" %in% names(policy_pages_nested)) {
    policy_pages_nested <- policy_pages_nested %>%
      mutate(sections = map(pageid, wiki_get_structure))
  }
  
  
  # Step 3: Create nested structure with all sections and their shortcuts
  policy_pages_nested <- policy_pages_nested %>%
    mutate(
      sections_with_shortcuts = pmap(list(sections, shortcut_sections), function(sects, shortcts) {
        # Expand sections
        section_df <- tibble(
          index = sects$index,
          line = sects$line
        )
        
        # If no shortcuts found, return sections with empty shortcuts
        if (is.null(shortcts) || nrow(shortcts) == 0) {
          return(section_df %>% mutate(shortcuts = list(character(0))))
        }
        
        # Join sections with shortcuts
        section_df %>%
          left_join(shortcts, by = c("line" = "heading")) %>%
          group_by(index, line) %>%
          summarise(
            shortcuts = list(na.omit(unique(shortcuts))),
            .groups = "drop"
          )
      })
    ) %>%
    select(pageid, page_title, self_shortcuts, sections_with_shortcuts)

    readr::write_rds(policy_pages_nested, "output/policy_pages_nested.rds")

    
  # Step 5: Expand and join to get policy parts
  all_subpolicies <- policy_pages_nested %>%
    select(pageid, page_title, sections_with_shortcuts) %>%
    unnest(sections_with_shortcuts) %>%
    # Filter to only sections with child shortcuts (or keep all if you want)
    dplyr::filter(lengths(shortcuts) > 0) %>%
    # Extract HTML content for each section
    mutate(
      policy_part = map2_chr(pageid, index, ~{
        wiki_get_html(.x, if (is.na(.y) || .y == "") NULL else .y)
      })
    ) 
  
  all_subpolicies <- all_subpolicies %>% 
    tibble::rowid_to_column()
  
    readr::write_rds(all_subpolicies, "output/all_subpolicies.rds")
}

  


```

## Labelling

https://sjgknight.com/assets/uploads/2022/08/taxonomy_full_aug2.pdf

4.1	Informant
Competence, motivations (interests and perspective)

4.2	Information
Evidence type, available evidence, input and output ambiguity

4.3	Uncertainty
Expert pertinence, human judgement, inherent uncertainty, tentative knowledge

What sources are used (informant - verification)
For what types of claim/information (uncertainty - representation)
With what strength of evidence (information - verification)


```{r addpolicylabels}


label_mapping <- tribble(
  ~key, ~statement, ~taxonony, ~onWiki, ~policyLink, ~notes, ~subtaxonomy,
  1, "What sources are used", "informant", "verification", c("Verifiability", "NOR", "Consensus", "Reliable sources"), "can relate to verification or representation, or their negotiation", c("competence", "motivations-interests", "motivations-perspective"),
  2, "For what types of claim", "information", "representation", c("NPOV", "Notability", "Due weight"), "relates to the types of claims included in the encyclopedia and their representation, i.e., consensus oriented, sourced, etc.", c("evidence type", "available evidence", "input ambiguity", "output ambiguity"),
  3, "With what strength of evidence", "uncertainty", "verification", c("MEDSCI", "MEDPOP", "MEDASSESS"), "relates to the assessment of evidence for claims, bound up with the kinds of claims that may be made/represented", c("expert pertinence", "human judgement", "inherent uncertainty", "tentative knowledge")
)

# Using the rowid, and the reactable created below. 

# Target can be one of: 
#(1) which is about the warrants for claims or verification
# inclusion, which is about what should / should not be included, 
#(2) representation, which is about how what is included should be representd, and 
#(3) negotiation, which is about how the process of editing is negotiated.

# The first two align broadly with the content guidelines in Wikipedia. '1' aligns also with notabilit and deletion. 
# The third aligns with the behavioural, editing, discussions guidelines.

policy_annotations <- tribble(
  ~rowid, ~key, ~target
  1, 1, "RS",
  2, 3, "relates to use of up-to-date evidence",
  3, 1, NA,
  4, 1, "negotiation",
  5, 1, "negotiation",
  7, "LOWRELEVANCE", "other-relates to sourcing information",
  8, "LOWRELEVANCE", "other-relates to sourcing information",
  14, "evidence type", "verification",
  15, "expert pertinence", "verification",
  16, "competence", "verification",
  18, "LOWRELEVANCE", "other-relates to sourcing information",
  26, "available evidence", "verification",
  27, "available evidence", "representation",
  28, "evidence type", "representation",
  39, "human judgement", "negotiation",
  40, "human judgement", "negotiation",
  64, "human judgement", "verification",
  65, "expert pertinence", "verification", #competence as in, what they are competent to speak to
  66, "LOWRELEVANCE", "other-relates to sourcing information",
  67, "LOWRELEVANCE", "other-relates to sourcing information",
  68, "expert pertinence", "verification",
  70, "compentence", "verification",
  71, "motivations", "verification",
  72, "competence", "verification",
  73, "competence", "verification",
  74, "expert pertinence", "verification",
  75, "compentence", "verification",
  76, "competence", "verification",
  79, "competence", "verification",
  80, "competence", "verification",
  82, "ambiguity", "verification",
  83, "human judgement", "representation"
)
  
  
  

# all_subpolicies <- DataEditR::data_edit(all_subpolicies)


```



## Analysis

```{r thanksclaude}

# Create a shared resources directory
shared_libdir <- "output/reactable_libs"

# ==============================================================================
# ANALYSIS 1: Table of article talk page content
# ==============================================================================

message("\n=== Creating Main Interactive Table ===\n")

table_talk2 <- results_filtered_content %>% 
#    dplyr::filter(content_filtered != "") %>%
    dplyr::mutate(timestamp = as.POSIXct(timestamp, format="%Y-%m-%dT%H:%M:%SZ", tz="UTC")) %>%
    dplyr::filter(timestamp < "2023-12-31T23:59:59Z") %>%
    create_interactive_table(displaytext = "content_html")

table_talk <- results_filtered_content %>%
#    dplyr::filter(content_filtered != "") %>%
    dplyr::mutate(timestamp = as.POSIXct(timestamp, format="%Y-%m-%dT%H:%M:%SZ", tz="UTC")) %>%
    dplyr::filter(timestamp < "2023-12-31T23:59:59Z") %>%
    create_interactive_table(displaytext = "content_filtered")

# export large html object
# Save tables using shared library directory
htmlwidgets::saveWidget(
  widget = table_talk,
  file = "output/table_talk.html",
  selfcontained = FALSE,
  libdir = shared_libdir
)


# ==============================================================================
# ANALYSIS 2: Table of policy content
# ==============================================================================

# Create summary reactable
table_policy <- all_subpolicies %>%
    dplyr::filter(lengths(shortcuts) > 0) %>% 
  select(rowid, page_title, line, shortcuts, policy_part) %>%
  reactable(
    columns = list(
      page_title = colDef(
        name = "Page",
        html = TRUE,
        cell = function(value, index) {
          pageid <- all_subpolicies$pageid[index]
          sprintf('<a href="https://en.wikipedia.org/?curid=%s" target="_blank">%s</a>',
                  pageid, value)
        }
      ),
      line = colDef(name = "Section"),
      index = colDef(name = "Index"),
      child_shortcuts = colDef(show = FALSE),
      child_shortcuts_str = colDef(
        name = "Shortcuts",
        html = TRUE,
        filterable = TRUE
      ),
      policy_part = colDef(
        name = "Policy Section",
        html = TRUE,
        minWidth = 800,
        cell = function(value, index) {
          sprintf('
            <div class="content-container">
              <button onclick="this.nextElementSibling.classList.toggle(\'collapsed\')"
                      style="margin-bottom: 6px; padding: 3px 6px; cursor: pointer;">
                Toggle Section
              </button>
              <div class="content-box"
                   style="max-height: 350px; overflow-y: auto; border: 1px solid #ccc; padding: 10px;">
                %s
              </div>
            </div>
            <style>.collapsed { display: none; }</style>
          ', value)
        }
      )
    ),

    defaultPageSize = 200,
    pagination = TRUE,
    highlight = TRUE,
    compact = TRUE,
    filterable = TRUE,
    searchable = TRUE,
    defaultColDef = colDef(
      align = "left",
      headerStyle = list(background = "#f7f7f8")
    )
  )


# export large html object
htmlwidgets::saveWidget(
  widget = table_policy,
  file = "output/table_policy.html",
  selfcontained = FALSE,
  libdir = shared_libdir
)

# ==============================================================================
# ANALYSIS 3: POLICY SUMMARY TABLE
# ==============================================================================

# Basic summary
summary <- create_policy_summary(results_filtered_content)

# Detailed analysis
detailed <- create_detailed_policy_summary(results_filtered_content)
detailed$overall
detailed$by_article
detailed$policy_cooccurrence

# Policy shortcut is in my policy_pages list but not used anywhere in my data
detailed$overall %>% 
  filter(!Policy %in% unlist(policy_pages$shortcuts))

# Policy shortcut is used in Talk page but isn't in my policy_pages list
policy_pages %>% 
  filter(!shortcuts %in% detailed$overall$Policy)


# Filter to only your searched policies
core_only <- filter_core_policies(summary, policies_core)

# Create summary reactable
table_policy_summary <- reactable(
  summary,
  columns = list(
    Policy = colDef(
      name = "Wikipedia Policy", 
      minWidth = 200,
      style = list(fontWeight = "500")
    ),
    Count = colDef(
      name = "Usage Count", 
      width = 150,
      style = list(fontWeight = "bold"),
      cell = function(value) {
        # Add bar chart visualization
        width <- paste0(value * 100 / max(policy_summary$Count), "%")
        bar_chart <- sprintf(
          '<div style="background: #e0e0e0; width: 100%%; height: 20px; border-radius: 3px;">
             <div style="background: #3498db; width: %s; height: 100%%; border-radius: 3px;"></div>
           </div>
           <span style="margin-left: 5px;">%d</span>',
          width, value
        )
        bar_chart
      },
      html = TRUE
    )
  ),
  searchable = TRUE,
  defaultPageSize = 20,
  highlight = TRUE,
  bordered = TRUE,
  striped = TRUE,
  defaultColDef = colDef(
    headerStyle = list(background = "#f7f7f8", fontWeight = "bold")
  )
)

# export large html object
htmlwidgets::saveWidget(
  widget = table_policy_summary,
  file = "output/table_policy_summary.html",
  selfcontained = FALSE,
  libdir = shared_libdir
)

# ==============================================================================
# ANALYSIS 4: ADDITIONAL STATISTICS
# ==============================================================================

message("\n=== Additional Statistics ===\n")

# Articles by number of policy references
article_stats <- results_filtered_content %>%
  mutate(article = str_extract(title, "(?<=Talk:)[^/]+")) %>%
  group_by(article) %>%
  summarise(
    n_edits = n_distinct(pageid),
    total_policies = sum(num_policies),
    avg_policies_per_pagestate = mean(num_policies),
    .groups = "drop"
  ) %>%
  arrange(desc(total_policies))

print(article_stats)

# Most common policy combinations
policy_combinations <- results_filtered_content %>%
  filter(num_policies >= 2) %>%
  mutate(
    policy_combo = map_chr(wp_policies, ~ paste(sort(.x), collapse = " + "))
  ) %>%
  count(policy_combo, sort = TRUE) %>%
  head(10)

message("\nTop 10 Policy Combinations:")
print(policy_combinations)

# ==============================================================================
# OUTPUT TABLES
# ==============================================================================

message("\n" , strrep("=", 80))
message("DISPLAYING RESULTS")
message(strrep("=", 80), "\n")

# Display summary table
message("1. POLICY USAGE SUMMARY\n")
summary_table

# Display main table
message("\n2. DETAILED TALK PAGE ANALYSIS\n")
main_table


# ==============================================================================
# EXPORT OPTIONS (optional)
# ==============================================================================

write.csv(policy_summary, "output/policy_summary.csv", row.names = FALSE)
write.csv(article_stats, "output/article_statistics.csv", row.names = FALSE)

message("\n✓ Analysis complete!")


```



```{r table}
pacman::p_load(reactable)

results_with_content %>%
  dplyr::filter(timestamp < "2023-12-31T23:59:59Z") %>%
  select(title, pageid, content_html) %>%
  reactable(
  columns = list(
    pageid = colDef(name = "Page ID"),
    title = colDef(
      name = "Title",
      cell = function(value, index) {
        # Make the title a clickable link to the Wikipedia page
        sprintf('<a href="https://en.wikipedia.org/?curid=%s" target="_blank">%s</a>',
                results_with_content$pageid[index], value)
      },
      html = TRUE
    ),
    content_html = colDef(
      name = "Content",
      html = TRUE,
      width = 900
    )
  ),
  searchable = TRUE,
  filterable = TRUE,
  pagination = TRUE,
  defaultPageSize = 150,
  highlight = TRUE,
  compact = TRUE
)


```
